Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-15 doc/manuscript/ESSDmanuscript.Rmd
add some info

>>>>

Documented at https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/defining_land_subcategory.md, https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/IPCC_LandUse_mapping.csv, and in [issue #8](https://github.com/forc-db/IPCC_database_integration/issues/8).

Land classification under UNFCCC (e.g., https://cbmjournal.biomedcentral.com/articles/10.1186/s13021-018-0095-3) is (i) defined differently across countries and (ii) probably not defined the same way as it might be defined in publications included in ForC.
Therefore, we do not transfer any classification of land as managed/unmanaged, but do provide any auxiliary info that may be useful in making this determination.

### 2021-06-15 doc/manuscript/ESSDmanuscript.tex
add some info

>>>>

Documented at
https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB\_mapping/defining\_land\_subcategory.md,
https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB\_mapping/IPCC\_LandUse\_mapping.csv,
and in
\href{https://github.com/forc-db/IPCC_database_integration/issues/8}{issue
\#8}.

Land classification under UNFCCC (e.g.,
https://cbmjournal.biomedcentral.com/articles/10.1186/s13021-018-0095-3)
is (i) defined differently across countries and (ii) probably not
defined the same way as it might be defined in publications included in
ForC. Therefore, we do not transfer any classification of land as
managed/unmanaged, but do provide any auxiliary info that may be useful
in making this determination.
